---
title: "Experiment 3 Stimuli"
author: "Bethany Gardner"
date: "06/10/2022"
output: 
  github_document:
    toc: true
    toc_depth: 3
  pdf_document:
    toc: true
    toc_depth: 3
    df_print: kable
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
options(dplyr.summarise.inform = FALSE)
library(magrittr)
library(kableExtra)
```

# Introductions to characters

```{r}
d_char <- read.csv("exp3_stim_char.csv", 
                   fileEncoding="UTF-8-BOM", stringsAsFactors=TRUE)
str(d_char) 
```

## Stimuli file structure

-   group = list assignment for PCIbex

-   trial_id = unique code across all conditions/lists/experiment
    sections

-   condition = between-subjects conditions (Nametag x Introduction)

-   character_set = 6 sets of characters

-   target_pronoun = character's pronouns (calling these variables
    "target" to match other stimuli lists)

-   target_id = character code that can reconstruct set, image, name,
    pronouns

-   target_image = character image (HT1, HT2, HT3, ST1, ST2, ST3)

-   target_name = character name (Brian, Dan, Emily, Jess, Alex, Sam)

-   target_file = file name for character image (image_pronoun_name.png
    or image_pronoun_name_nametag.png, according to condition)

-   brother = file name for character's brother
    (character-image_brother_character-name.png)

-   sister = file name for character's sister
    (character-image_sister_character-name.png)

-   text1_name = text to display with character image ("This is [name]"

-   text1_pronouns = text to display with character image ("." or ", who
    uses [pronouns].", according to condition)

-   text2_brother = text to display with brother image ("He has/she
    has/they have a brother."

-   text3_sister = text to display with sister image ("And he has/and
    she has/and they have a sister.")

## Conditions/lists

Split into 4 conditions:

1.  Both = +Nametag, +Introduction
2.  Intro = -Nametag, +Introduction
3.  Nametag = +Nametag, -Introduction
4.  Neither = -Nametag, -Introduction

```{r}
summary(d_char$condition)
```

Counter-balanced with 6 lists of characters:

```{r}
d_char$character_set %>% as.factor() %>% summary()
```

6 sets of characters -\> 6 of each pronoun type, each of which appears
1x in each of the 4 conditions.

```{r}
d_char %>% count(target_pronoun, target_id)
```

4 conditions x 6 character lists = 24 groups, each of which has 3 trials
(1 he/him character, 1 she/her character, 1 they/them character).

```{r}
d_char %>% group_by(group) %>% summarise(n())
```

## Character image

Check to make the image displayed matches the condition/list variables:

```{r}
d_char %<>% 
  mutate(.after="target_file", target_path=str_c(
      target_image, "_",
      case_when(
          target_pronoun=="he/him"    ~ "he",
          target_pronoun=="she/her"   ~ "she",
          target_pronoun=="they/them" ~ "they"),
      "_", target_name,
      case_when(
          condition=="both"|condition=="nametag"  ~ "_nametag",
          condition=="intro"|condition=="neither" ~ ""),
      ".png")) %>%
   mutate(.after="target_path", 
      target_file_check=(target_file==target_path))

summary(d_char$target_file_check)
```

## Character text

Check that text displayed matches the condition/list variables:

"This is [name]"

```{r}
d_char %<>% mutate(.after=14, text1_name_check=
  str_detect(as.character(text1_name),      
             str_to_sentence(target_name)))

summary(d_char$text1_name_check)
```

+Introduction conditions: ", who uses [pronouns]."

-Introduction conditions: "."

```{r}
d_char %<>% mutate(.after="text1_pronouns", 
      text1_pronouns_check=case_when(
          (condition=="nametag" | condition=="neither") ~
              text1_pronouns==".",
          (condition=="both" | condition=="intro") ~ 
              str_detect(as.character(text1_pronouns), 
               as.character(target_pronoun))))

summary(d_char$text1_pronouns_check)
```

## Sibling images

Check that sibling images displayed match the character variables
(image, name):

```{r}
d_char %<>% mutate(.after="brother", 
      brother_path=str_c(
          target_image, "_brother_", target_name, ".png")) %>%
      mutate(.after="brother_path", 
      brother_check=(brother==brother_path))

summary(d_char$brother_check)
```

```{r}
d_char %<>% mutate(.after="sister", 
      sister_path=str_c(
          target_image, "_sister_", target_name, ".png")) %>%
      mutate(.after="sister_path", 
      sister_check=(sister==sister_path))

summary(d_char$sister_check)
```

## Sibling text

Check that text displayed matches character variables (pronoun).

"[Pronoun] has a brother."

```{r}
d_char$text2_brother %<>% as.character()

d_char %<>% mutate(.after="text2_brother", text2_brother_check=
    ((target_pronoun=="he/him" && 
        str_detect(text2_brother, "He has")) |
    (target_pronoun=="she/her" && 
        str_detect(text2_brother, "She has")) |
    (target_pronoun=="they/them" && 
        str_detect(text2_brother, "They have"))) &&
    str_detect(text2_brother, "a brother."))

summary(d_char$text2_brother_check)
```

"And [pronoun] has a sister."

```{r}
d_char$text3_sister %<>% as.character()

d_char %<>% mutate(.after="text3_sister", text3_sister_check=
    ((target_pronoun=="he/him" && 
        str_detect(text3_sister, "And he has")) |
    (target_pronoun=="she/her" && 
        str_detect(text3_sister, "And she has")) |
    (target_pronoun=="they/them" && 
        str_detect(text3_sister, "And they have"))) &&
  str_detect(text3_sister, "a sister."))

summary(d_char$text3_sister_check)
```

# Production prompt displays

## Stimuli file structure

```{r}
d <- read.csv("exp3_stimuli_all.csv", stringsAsFactors=TRUE)

str(d)
```

Experiment variables:

-   group = list assignment for PCIbex

-   trial_id = unique code across all conditions/lists/experiment
    sections

-   condition = between-subjects conditions (Nametag x Introduction)

-   character_set = 6 sets of characters

Target character (the one described) variables:

-   target_pronoun = character's pronouns

-   target_id = character code that can reconstruct set, image, name,
    pronouns

-   target_image = character image (HT1, HT2, HT3, ST1, ST2, ST3)

-   target_name = character name (Brian, Dan, Emily, Jess, Alex, Sam)

-   target_file = file name for character image (image_pronoun_name.png
    or image_pronoun_name_nametag.png, according to condition)

-   target_x = location (275=left, 525=right)

Distractor character (pictured, but not described) variables:

-   distractor_pronoun = character's pronouns

-   distractor_id = character code that can reconstruct set, image,
    name, pronouns

-   distractor_image = character image (HT1, HT2, HT3, ST1, ST2, ST3)

-   distractor_name = character name (Brian, Dan, Emily, Jess, Alex,
    Sam)

-   distractor_file = file name for character image
    (image_pronoun_name.png or image_pronoun_name_nametag.png, according
    to condition)

-   distractor_x = location (275=left, 525=right)

Object variables:

-   object_x: object horizontal location (175=left, 725=right)

-   object_y2, object_y3, object_y4: object vertical path. (starts at
    center, 150 100 50 moves up, 250 300 350 moves down)

Sibling variables:

-   sibling_image: sibling that receives object

-   top_left, top_right, bottom_left, bottom_right: all 4 sibling images
    to display

Correct answer:

-   correct_description: [name] gave the [object] to [pronoun] [sibling]

-   audio: audio file for example and practice trials

## Conditions/lists

Split into 4 conditions:

1.  Both = +Nametag, +Introduction
2.  Intro = -Nametag, +Introduction
3.  Nametag = +Nametag, -Introduction
4.  Neither = -Nametag, -Introduction

```{r}
summary(d$condition)
```

Counter-balanced with 6 lists of characters:

```{r}
d$character_set %>% as.factor() %>% summary()
```

6 sets of characters \* 3 pronouns = 18 character variations, each with
a unique image-pronoun-name combination.

```{r}
d %>% select(target_id, target_pronoun, 
             target_image, target_name) %>%
  unique() %>% arrange(target_id)
```

4 conditions x 6 character lists = 24 groups, each of which has 3 trials
(1 he/him character, 1 she/her character, 1 they/them character). The
Nametag, but not the Introduction condition varies here, but need the
items repeated to keep group assignment consistent in PCIbex.

36 = 3 example + 3 practice + 30 test trials per group

```{r}
d %>% group_by(group) %>% summarise(n())
```

```{r}
d %<>% mutate(.after="group", trial_type=case_when(
  str_detect(trial_id, "example") ~ "example",
  str_detect(trial_id, "practice") ~ "practice",
  str_detect(trial_id, "test") ~ "test"))
summary(as.factor(d$trial_type))
```

Each trial has a unique ID, to double-check that no trial info is lost.

```{r}
str(d$trial_id)
864/36
```

## Characters

### Pronouns

Each list has 1 example, 1 practice, and 10 test trials for each pronoun
type.

```{r}
d %>% count(group, target_pronoun, trial_type)
```

The distractor character pronouns are split evenly between the other two
pronoun types.

```{r}
d %>% count(distractor_pronoun, target_pronoun)  
```

### Images

6 character images.

```{r}
summary(d$target_image)
summary(d$distractor_image)
```

Each list contains 3 images.

```{r}
d %>% count(character_set, target_image) 
d %>% count(character_set, distractor_image) 
```

Each image appears 2x with he/she and 1x with they.

```{r}
d %>% count(target_image, target_pronoun) 
d %>% count(distractor_image, distractor_pronoun) 
```

### Names

6 names (2 masc, 2 fem, 2 androgynous).

```{r}
summary(d$target_name)
summary(d$distractor_name)
```

Each list has 3 names (1 masc, 1 fem, 1 androgynous).

```{r}
d %>% count(character_set, target_name) 
d %>% count(character_set, distractor_name) 
```

Masculine names appear 2x with he/him and 1x with they/them. Feminine
names appear 2x with she/her and 1x with they/them. Androgynous names
appear 1x with he/him, 1x with she/her, and 1x with they/them. [1x = (1
practice + 1 example + 10 test) x 4 conditions]

```{r}
d %>% count(target_name, target_pronoun) 
d %>% count(distractor_name, distractor_pronoun) 
```

## Siblings

Image for sibling that receives object matches character.

```{r}
d %>% mutate(sibling_group=str_sub(sibling_image, 0, 11)) %>%
  count(target_image, sibling_group) 
```

### Example & practice trials

Odd numbers mean that example+practice trials aren't perfectly balanced,
so less confusing to check test trials separately.

Sibling that receives object is distributed evenly.

```{r}
d %>% filter(trial_type=="example"|trial_type=="practice") %>% 
  mutate(sibling_group=str_sub(sibling_image, 0, 11)) %>%
  group_by(sibling_group) %>%
  summarise(n=n()) 
```

Target characters that appear on the left (1/3 of example, 2/3 of
practice) have matching sibling images.

```{r}
d %>% filter(trial_type=="example"|trial_type=="practice") %>% 
  filter(target_x==275) %>% 
  mutate(sibling_group=str_sub(top_left, 0, 11)) %>%
  count(target_image, sibling_group)

d %>% filter(trial_type=="example"|trial_type=="practice") %>% 
  filter(target_x==275) %>% 
  mutate(sibling_group=str_sub(bottom_left, 0, 11)) %>%
  count(target_image, sibling_group) 
```

Target characters that appear on the right (2/3 example, 1/3 of practice
trials) have matching sibling images.

```{r}
d %>% filter(trial_type=="example"|trial_type=="practice") %>% 
  filter(target_x==525) %>% 
  mutate(sibling_group=str_sub(top_right, 0, 11)) %>%
  count(target_image, sibling_group) 

d %>% filter(trial_type=="example"|trial_type=="practice") %>% 
  filter(target_x==525) %>% 
  mutate(sibling_group=str_sub(bottom_right, 0, 11)) %>%
  count(target_image, sibling_group) 
```

Distractor characters that appear on the left (2/3 example, 1/3 of
practice trials) have matching sibling images.

```{r}
d %>% filter(trial_type=="example"|trial_type=="practice") %>% 
  filter(distractor_x==275) %>% 
  mutate(sibling_group=str_sub(top_left, 0, 11)) %>%
  count(distractor_image, sibling_group) 

d %>% filter(trial_type=="example"|trial_type=="practice") %>% 
  filter(distractor_x==275) %>% 
  mutate(sibling_group=str_sub(bottom_left, 0, 11)) %>%
  count(distractor_image, sibling_group) 
```

Distractor characters that appear on the right (1/3 of example, 2/3 of
practice trials) have matching sibling images.

```{r}
d %>% filter(trial_type=="example"|trial_type=="practice") %>% 
  filter(distractor_x==525) %>% 
  mutate(sibling_group=str_sub(top_right, 0, 11)) %>%
  count(distractor_image, sibling_group) 

d %>% filter(trial_type=="example"|trial_type=="practice") %>% 
  filter(distractor_x==525) %>% 
  mutate(sibling_group=str_sub(bottom_right, 0, 11)) %>%
  count(distractor_image, sibling_group) 
```

### Test trials

Sibling that receives object is distributed evenly.

```{r}
d %>% filter(trial_type=="test") %>%
  group_by(sibling_image) %>%
  summarise(n=n()) 
```

Target characters that appear on the left have matching sibling images,
split as evenly as possible between brother and sister.

```{r}
d %>% filter(trial_type=="test") %>% 
  filter(target_x==275) %>% 
  mutate(sibling_group=str_sub(top_left, 0, 11)) %>%
  count(target_image, sibling_group)

d %>% filter(trial_type=="test") %>% 
  filter(target_x==275) %>% 
  mutate(sibling_group=str_sub(bottom_left, 0, 11)) %>%
  count(target_image, sibling_group) 
```

Target characters that appear on the right have matching sibling images,
split as evenly as possible between brother and sister.

```{r}
d %>% filter(trial_type=="test") %>% 
  filter(target_x==525) %>% 
  mutate(sibling_group=str_sub(top_right, 0, 11)) %>%
  count(target_image, sibling_group) 

d %>% filter(trial_type=="test") %>% 
  filter(target_x==525) %>% 
  mutate(sibling_group=str_sub(bottom_right, 0, 11)) %>%
  count(target_image, sibling_group) 
```

Trials where distractor character is on left have matching sibling
images.

```{r}
d %>% filter(trial_type=="test") %>% 
  filter(distractor_x==275) %>% 
  mutate(sibling_group=str_sub(top_left, 0, 11)) %>%
  count(distractor_image, sibling_group)  

d %>% filter(trial_type=="test") %>% 
  filter(distractor_x==275) %>% 
  mutate(sibling_group=str_sub(bottom_left, 0, 11)) %>%
  count(distractor_image, sibling_group)  
```

Trials where distractor character is on right have matching sibling
images.

```{r}
d %>% filter(trial_type=="test") %>%
  filter(distractor_x==525) %>% 
  mutate(sibling_group=str_sub(top_right, 0, 11)) %>%
  count(distractor_image, sibling_group)  

d %>% filter(trial_type=="test") %>% 
  filter(distractor_x==525) %>% 
  mutate(sibling_group=str_sub(bottom_right, 0, 11)) %>%
  count(distractor_image, sibling_group)  
```

## Objects

36 objects, 1 for each trial frame (3 + 3 + 30).

```{r}
d %>% group_by(trial_type, object_image) %>% summarise(n())
```

Check that object starts on same side as target character.

```{r}
d %<>% mutate(.after="object_x", object_x_check=case_when(
  target_x==275 ~ object_x==175,
  target_x==525 ~ object_x==725))
summary(d$object_x_check)
```

Check that object moves up/down to the correct sibling.

```{r}
d %<>% mutate(.after="sibling_image", sibling_pos=case_when(
    sibling_image==top_left ~ "top left",
    sibling_image==top_right ~ "top right",
    sibling_image==bottom_left ~ "bottom left",
    sibling_image==bottom_right ~ "bottom right")) 
```

```{r}
d %<>% mutate(.after="object_y4", object_y_check=case_when(
  str_detect(sibling_pos, "top") ~ 
    (object_y2==150 & object_y3==100 & object_y4==50),
  str_detect(sibling_pos, "bottom") ~
    (object_y2==250 & object_y3==300 & object_y4==350)))

summary(d$object_y_check)
```

## Counterbalance positioning

### Target character

Target character position (left or right) counterbalanced across 3
example, 3 test, and 30 practice trials.

```{r}
d %>% count(trial_type, target_x)  
```

```{r}
d %>% count(character_set, target_x)  
```

### Sibling & object position

Sibling/object counterbalanced. (Just checking test trials b/c can't
balance 3 test and 3 practice across 4 positions.)

```{r}
d %>% filter(trial_type=="test") %>%
  group_by(character_set) %>%
  count(sibling_pos)  
```

## Correct answer

Equal number of his/her/their brother/sister correct answers per list.

```{r}
d %<>% mutate(.after="sibling_image", sibling_type=case_when(
  str_detect(sibling_image, "brother") ~ "brother",
  str_detect(sibling_image, "sister") ~ "sister"))

d %>% group_by(character_set) %>% 
  count(target_pronoun, sibling_type)  
```

Double check correct description ("[Name] gave the [object] to
[pronoun][sibling].")

```{r}
d %<>% mutate(.after="correct_description", 
  correct_description_check=
  str_c(str_to_sentence(target_name), 
        " gave the ",
        str_sub(object_image, end=-5),
        " to ",
        case_when(
          target_pronoun=="he/him" ~ "his ",
          target_pronoun=="she/her" ~ "her ",
          target_pronoun=="they/them" ~ "their "),
        case_when(
          str_detect(sibling_image, "brother") ~ "brother.",
          str_detect(sibling_image, "sister") ~ "sister."))) %>%
  mutate(.after="correct_description_check",
         correct_description_compare=
        (correct_description==correct_description_check))
summary(d$correct_description_compare)
```

## Correct file names

### Target

```{r}
d %<>% mutate(.after="target_file", target_path=
          str_c(target_image, "_",
          case_when(
              target_pronoun=="he/him"    ~ "he",
              target_pronoun=="she/her"   ~ "she",
              target_pronoun=="they/them" ~ "they"),
          "_", target_name,
          case_when(
              condition=="both" | condition=="nametag"  ~ "_nametag",
              condition=="intro" | condition=="neither" ~ ""),
          ".png")) %>%
       mutate(.after="target_path",
              target_path_check=(target_file==target_path))

summary(d$target_path_check)
```

### Distractor

```{r}
d %<>% mutate(.after="distractor_file", distractor_path=
          str_c(distractor_image, "_",
          case_when(
              distractor_pronoun=="he/him" ~ "he",
              distractor_pronoun=="she/her" ~ "she",
              distractor_pronoun=="they/them" ~ "they"),
          "_", distractor_name,
          case_when(
              condition=="both"|condition=="nametag" ~ "_nametag",
              condition=="intro"|condition=="neither" ~ ""),
          ".png")) %>%
  mutate(.after="distractor_path", 
         distractor_path_check=(distractor_file==distractor_path))

summary(d$distractor_path_check)
```

### Sibling

```{r}
d %<>% mutate(.after="sibling_image", sibling_path=str_c(
            target_image, "_", sibling_type, "_", 
            target_name, ".png")) %>%
       mutate(.after="sibling_path", sibling_path_check=
            (sibling_image==sibling_path))
 
summary(d$sibling_path_check)
```

### Audio

```{r}
d$audio %<>% as.factor() %>% na_if("")
```

144 example and practice trials have audio; 720 test trials don't.
```{r}
d %<>% mutate(.after="audio", audio_path=case_when(
       trial_type=="example" | trial_type=="practice" ~ 
         (str_c(trial_type, "_", 
                target_name, "-",
                str_sub(object_image, end=-5), "-",
                case_when(
                    target_pronoun=="he/him" ~ "his",
                    target_pronoun=="she/her" ~ "her",
                    target_pronoun=="they/them" ~ "their"),
                "-", sibling_type, ".mp3")),
       trial_type=="test" ~ ""))
d$audio_path %<>% na_if("")

d %<>% mutate(.after="audio_path", audio_path_check=
       (audio==audio_path))
summary(d$audio_path_check)

```

# List of stimuli

## Images

Full list of image files called in the stimuli list:

```{r}
image_list <- d %>% 
  select(target_file, distractor_file, object_image,
    sibling_image, top_left, top_right, bottom_left, bottom_right) %>%
  pivot_longer(cols=everything(), 
               names_to="temp", 
               values_to="file_name") 

image_list2 <- d_char %>% 
  select(target_file, brother, sister) %>%
  pivot_longer(cols=everything(), 
               names_to="temp", 
               values_to="file_name") 

image_list %<>% bind_rows(image_list2) %>%
  arrange(file_name) %>%
  select(-temp) %>%
  unique() 
  
```

Check to make sure they're all there:

```{r}
files <- list.files("Images/Characters_300px/", pattern="*.png") 
files %<>% append(list.files("Images/Objects_300px/", pattern="*.png"))

image_list %<>% mutate(exist=file_name %in% files) 

image_list  
```

## Audio

List of audio files for example and practice trials.

```{r}
audio_list <- d %>% select(audio) %>% 
  drop_na() %>% unique()
```

Check to make sure they're all there:

```{r}
recordings <- list.files("Audio/", pattern="*.mp3") 

audio_list %<>% mutate(exist=audio %in% recordings) 

audio_list  
```
